Compositional equivalences based on Open pNets

### 2020-07-10 2016-Weak-FH-Bisim/WeakBisim.tex
Reorganise la section related-work

\TODO{retravailler le paragraphe ci dessous}
In

\cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems. To improve scaling and compositionality, the authors  decouple the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables. These works clearly highlight the interest of incremental and compositional verification in a very general setting. By adding more structure to the composition model and designing a dedicated bisimulation theory, we show here how to enforce a compositional proof system that is more powerful than independent sets of variables. Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework. However, the models of Johnson et al. are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article. Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view. One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.

\TODO{Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,BuscemiM:08,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.}

\ERIC{J'ai copie/colle ici le Related Work que Zechen a mis dans notre
  papier bisim...
  Pas tres satisfaisant pour les aspects Weak, mais quelques inputs a
  regarder}

To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterised, with loops and assignments) system models, with providing fully complete algorithms.
For the sake of completeness, we give a brief overview of other Symbolic Bisimulation researches.

One line of research is providing Symbolic Bisimulation for different model or language. 
In Calder's work\cite{calder2001symbolic}, they define a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
Borgstrom et al., Delaune et al. and Buscemi et al. provide symbolic semantic and equivalence for different variants of pi calculus respectively\cite{borgstrom2004symbolic}\cite{delaune2007symbolic}\cite{buscemi2008open}, and later in 2012 Liu's work provided symbolic bisimulation  for full applied pi calculus\cite{liu2010complete};
The most recent work, Feng et al. provide a symbolic bisimulation for quantum processes
\cite{feng2014symbolic}.
All the above works, didn't give a complete approach for verification, and the models on which these works based are simpler or different than ours.

Another line of research is devising the algorithm for computing symbolic Bisimulation Equivalence.
In Dovier's work, they provide a rank-based algorithm, layering the input model to compute bisimulation\cite{dovier2002rank}. 
Baldan et al. also focus on open systems, using a logical programming language \emph{Prolog} to model the systems and compute Bisimulation\cite{baldan2001compositional}.
Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.

>>>>

To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterised, with loops and assignments) system models, with providing fully complete algorithms.
For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches.

\TODO{Logique de reorganisation: 1: Open et compositionel [15,13, peut-etre 17], 2: symbolic et data-sensitive [lin, rathke 4 et ?, 5, puis Lotos 18, Pi-calc 16,19,20,22, quantum 25.]}

\paragraph{Open and Compositional systems}

\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?}
In
\cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems. To improve scaling and compositionality, the authors  decouple the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables. These works clearly highlight the interest of incremental and compositional verification in a very general setting. By adding more structure to the composition model and designing a dedicated bisimulation theory, we show here how to enforce a compositional proof system that is more powerful than independent sets of variables. Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework. However, the models of Johnson et al. are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article. Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view. One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.

\TODO{Et ou on place celui-la: 
https://www.researchgate.net/publication/322674459\_Bisimulations\_on\_Data\_Graphs ?
}

\TODO{Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,Dubut:20} --verifier Dubut--, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.}

\paragraph{Symbolic and data-sensitive systems}

Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.

Research related to the keyword "Symbolic Bisimulation" refer to two very different domains, namely BDD-like techniques for modeling and computing finite-state bisimulations, that are not related to our topic; and symbolic semantics for data-dependant or high-order systems, that are very close in spirit to our approach. In this last area, we can mention
Calder's work \cite{calder2001symbolic}, that  defines a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
Borgstrom et al., Liu et al, Delaune et al. and Buscemi et al. providing symbolic semantic and equivalence for different variants of pi calculus respectively \cite{borgstrom2004symbolic,delaune2007symbolic,liu2010complete,buscemi2008open}; and more recently
 Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
All the above works, didn't give a complete approach for verification, and the models on which these works based are definitely different from ours.

% Another line of research is devising the algorithm for computing symbolic Bisimulation Equivalence.
% In Dovier's work, they provide a rank-based algorithm, layering the input model to compute bisimulation\cite{dovier2002rank}. 
% Baldan et al. also focus on open systems, using a logical programming language \emph{Prolog} to model the systems and compute Bisimulation\cite{baldan2001compositional}.
%Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
